Tensor denoising and completion based on ordinal observations

### 2020-06-06 paper/ICML/supplements/latexsource/ordinalTv4.tex
update
typo

\begin{table*}[ht]
\centerline{\includegraphics[width=.98\textwidth]{compare.pdf}}
\vspace{-.3cm}
\caption{Comparison with previous work. For ease of presentation, we summarize the error rate and sample complexity assuming equal tensor dimension in all modes. $K$: tensor order; $L$: number of ordinal levels; $d$: dimension at each mode. }~\label{tab:compare}
\vspace{-.7cm}
\end{table*}

@@

\begin{thm}~\label{thm:completion}
Assume the same set-up as in Theorem~\ref{thm:rate}. Suppose that we observe a subset of tensor entries $\{y_\omega\}_{\omega\in\Omega}$, where $\Omega$ is chosen at random with replacement according to a probability distribution $\Pi$. Let $\hat \Theta$ be the solution to~\eqref{eq:estimator}, and assume $r_{\max}=\tO(1)$. Then, with very high probability,
\[
\PiFnormSize{}{\Theta-\hat \Theta}^2 \to 0,\quad \text{ as }\quad {|\Omega|\over \sum_k d_k} \ \to \infty.
\]
\end{thm}
Theorem~\ref{thm:completion} shows that our estimator achieves consistent recovery using as few as $\tilde{\tO}(Kd)$ noisy, quantized observations from an order-$K$ $(d,\ldots,d)$-dimensional tensor. Note that $\tilde \tO(Kd)$ roughly matches the degree of freedom for an order-$K$ tensor of fixed rank $\mr$, suggesting the optimality of our sample requirement. This sample complexity substantially improves over earlier result $\tO(d^{\lceil K/2\rceil})$ based on square matricization~\cite{mu2014square}, or $\tO(d^{N/2})$ based on tensor nuclear-norm regularization~\cite{yuan2016tensor}. Existing methods that achieve $\tilde \tO(Kd)$ sample complexity require either a deterministic cross sampling design~\cite{zhang2019cross} or univariate measurements~\cite{ghadermarzy2018learning}. Our method extends the conclusions to multi-level measurements under a broader class of sampling schemes.

>>>>

\begin{table*}[ht]
\centerline{\includegraphics[width=1\textwidth]{compare.pdf}}
\vspace{-.3cm}
\caption{Comparison with previous work. For ease of presentation, we summarize the error rate and sample complexity assuming equal tensor dimension in all modes. $K$: tensor order; $L$: number of ordinal levels; $d$: dimension at each mode. }~\label{tab:compare}
\vspace{-.7cm}
\end{table*}

@@

\begin{thm}~\label{thm:completion}
Assume the same set-up as in Theorem~\ref{thm:rate}. Suppose that we observe a subset of tensor entries $\{y_\omega\}_{\omega\in\Omega}$, where $\Omega$ is chosen at random with replacement according to a probability distribution $\Pi$. Let $\hat \Theta$ be the solution to~\eqref{eq:estimator}, and assume $r_{\max}=\tO(1)$. Then, with very high probability,
\[
\PiFnormSize{}{\Theta-\hat \Theta}^2 \to 0,\quad \text{ as }\quad {|\Omega|\over \sum_k d_k} \ \to \infty.
\]
\end{thm}
Theorem~\ref{thm:completion} shows that our estimator achieves consistent recovery using as few as $\tilde{\tO}(Kd)$ noisy, quantized observations from an order-$K$ $(d,\ldots,d)$-dimensional tensor. Note that $\tilde \tO(Kd)$ roughly matches the degree of freedom for an order-$K$ tensor of fixed rank $\mr$, suggesting the optimality of our sample requirement. This sample complexity substantially improves over earlier result $\tO(d^{\lceil K/2\rceil})$ based on square matricization~\cite{mu2014square}, or $\tO(d^{K/2})$ based on tensor nuclear-norm regularization~\cite{yuan2016tensor}. Existing methods that achieve $\tilde \tO(Kd)$ sample complexity require either a deterministic cross sampling design~\cite{zhang2019cross} or univariate measurements~\cite{ghadermarzy2018learning}. Our method extends the conclusions to multi-level measurements under a broader class of sampling schemes.
